% resumo em inglês
\setlength{\absparsep}{18pt} % ajusta o espaçamento dos parágrafos do resumo
\begin{resumo}[Abstract]
\textit{Environment 3D reconstruction has being used in several fields, for example: The environment mapping for archeological research at areas where scientists can't reach, or compare one area before and after a catastrophe\cite{SLAMAP}, also in robot automatization so it can move in an environment and now, one of it most recent uses is virtual reality for games. Unfortunately, it still has some limitations, since the camera used influentiates greatly on the result (besides the fact it must be well calibrated). Usually for mapping, several cameras are used, in order to obtain many point of view for the same object, in a similar fashion as human eyes perceive the environment, and several techniques and procedures exist to realize the mapping with only one camera with the help of Multiple View Geometry. The goal of this work is to use these concepts in order to obtain the reconstruction of an environment, initially using a smartphone, resulting in the PhotoGuide app. That app recognizes keypoints from a video of directly from the camera, but due to performance problems, was needed shift the process to more powerful machines, as a desktop, and change the reconstruction tool to LSD-SLAM, which provides the full suite of 3D reconstruction tools.

Normalmente para o mapeamento, são utilizadas várias câmeras, para obter diversos pontos de vista para um mesmo objeto (semelhante à como os olhos humanos percebem o ambiente), e há técnicas e procedimentos para realizar o mapeamento com apenas uma câmera com a ajuda da \textit{Multiple View Geometry}. O objetivo deste trabalho é utilizar tais fundamentos para obter a reconstrução do ambiente, inicialmente de um \textit{smartphone}, resultando no aplicativo PhotoGuide. Tal aplicativo reconhece keypoints de um vídeo ou diretamente da câmera, mas por problemas de desempenho, foi necessário mover o processamento para máquinas mais poderosas, como um \textit{desktop} trocando a ferramenta de reconstrução para o \textit{LSD-SLAM}, que fornece um pacote completo de ferramentas para reconstruções 3D. 
% \end{otherlanguage*}
\textit{\textbf{keywords}: 3D Reconstruction. LSD-SLAM. Images processing. Environment mapping}.
\end{resumo}